The genomic impacts of drift and selection for hybrid performance in maize

### 2015-08-26 main.tex
Fig 5 caption now states 99% quantile

\begin{figure*}[tb]   
   \includegraphics[width=0.7\linewidth]{Fig_S1_combined.pdf}
   \caption{Heterozygosity in each population, observed vs. simulated data. Heterozygosity was calculated as the average across all markers genome-wide  in the BSSS (A)  and BSCB1 (B) populations. The observed data is marked by the red line, the simulations by gray dots, and the median of the simulations by a green dot. \rev{Black lines represent the 95\% quantiles of the simulated data.} } 
    \label{fig:compare_to_sims}
\end{figure*}

Averaged across the genome, the vast majority of the reduction in diversity observed in both populations can be attributed to genetic drift. 
Nonetheless, we do observe \rev{differences from values generated under our neutral simulations} (Figure \ref{fig:compare_to_sims})\jri{is my interpretation of the black lines in figure correct?}. 
The observed data show higher than expected heterozygosity at cycle 4, \rev{which could be explained by several factors, including differences between simulated and actual breeding practices, under-sampling of diversity in cycle 0, selection acting to increase the frequency of initially rare haplotypes, or even selection acting to maintain heterozygosity \citep[e.g.][]{McMullen2009,Gore2009a} } \jri{where is this excess of diversity? if it's all pericentromeric can we argue for the first hypothesis?}

>>>>

\begin{figure*}[tb]   
   \includegraphics[width=0.7\linewidth]{Fig_S1_combined.pdf}
   \caption{Heterozygosity in each population, observed vs. simulated data. Heterozygosity was calculated as the average across all markers genome-wide  in the BSSS (A)  and BSCB1 (B) populations. The observed data is marked by the red line, the simulations by gray dots, and the median of the simulations by a green dot. \rev{Black lines represent the 99\% and 1\% quantiles of the simulated data.} } 
    \label{fig:compare_to_sims}
\end{figure*}

Averaged across the genome, the vast majority of the reduction in diversity observed in both populations can be attributed to genetic drift. 
Nonetheless, we do observe \rev{differences from values generated under our neutral simulations} (Figure \ref{fig:compare_to_sims})
The observed data show higher than expected heterozygosity at cycle 4, \rev{which could be explained by several factors, including differences between simulated and actual breeding practices, under-sampling of diversity in cycle 0, selection acting to increase the frequency of initially rare haplotypes, or even selection acting to maintain heterozygosity \citep[e.g.][]{McMullen2009,Gore2009a} } \jri{where is this excess of diversity? if it's all pericentromeric can we argue for the first hypothesis?}
